A Hexagon Tile Map Algorithm for Displaying Spatial Data

### 2020-10-05 kobakian-cook.tex
Fix name repair in sugarbag, then update

\begin{Schunk}
\begin{Sinput}
states <- absmapsdata::state2011 %>% 
  rmapshaper::ms_simplify(keep = 0.25, keep_shapes = TRUE) %>% 
  filter(!state_name_2011 == "Other Territories")

sa2 <- absmapsdata::sa22011 %>% 
  filter(state_name_2011 == "New South Wales") %>% 
  filter(!st_is_empty(geometry))

@@

aus_ggchoro <- ggplot(sa2thyroid_ERP) + 
  #geom_sf(fill = "lightgrey", data = states) + 
  geom_sf(aes(fill = SIR)) + 
  scale_fill_identity()
\end{Sinput}
\end{Schunk}

\begin{Schunk}
\begin{Sinput}
###############################################################################

sa2thyroid_ERP <- st_transform(sa2thyroid_ERP, 3112)
sa2thyroid_ERP <- sa2thyroid_ERP %>% 
  mutate(sva = sqrt(as.numeric(Population)/as.numeric(albers_sqkm)))

@@

aus_ggcont <- ggplot(cont) + 
  geom_sf(aes(fill = SIR), colour = NA) + 
  scale_fill_identity() + 
  invthm + guides(fill=FALSE)
aus_ggcont

ggsave(filename = "figures/aus_ggcont.png", plot = aus_ggcont,
       device = "png", bg = "transparent", dpi = 300,  width = 7, height = 6)
\end{Sinput}
\end{Schunk}

@@

aus_ggncont <- ggplot(ncont) + 
  geom_sf(aes(fill = SIR), colour = NA) + 
  scale_fill_identity() + 
  invthm + guides(fill=FALSE)
aus_ggncont

ggsave(filename = "figures/aus_ggncont.png", plot = aus_ggncont,
       device = "png", bg = "transparent", dpi = 300,  width = 7, height = 6)
\end{Sinput}
\end{Schunk}

@@

dorl <- sa2lung_ERP %>%
  mutate(pop = (Population/max(Population))*10) %>% 
  cartogram_dorling(., k = 0.01, weight = "pop", m_weight = 1) %>% st_as_sf()
d <- st_bbox(dorl)
aus_ggdorl <- ggplot(dorl) + 
  geom_sf(aes(fill = SIR)) + 
  scale_fill_identity()+
  invthm + guides(fill = FALSE)
aus_ggdorl

ggsave(filename = "figures/aus_ggdorl.png", plot = aus_ggdorl,
       device = "png", bg = "transparent", dpi = 300,  width = 7, height = 6)
\end{Sinput}
\end{Schunk}

\begin{Schunk}
\begin{Sinput}
## Load data
tas_sa2 <- absmapsdata::sa22011 %>% 
  filter(state_name_2011 == "New South Wales")

## Create centroids set
centroids <- create_centroids(tas_sa2, "sa2_name_2011")

## Create hexagon grid
grid <- create_grid(centroids = centroids,
                    hex_size = 0.12,
                    buffer_dist = 1.2)

## Allocate polygon centroids to hexagon grid points
hex_allocated <- allocate(
  centroids = centroids,
  hex_grid = grid,
  sf_id = "sa2_name_2011",
  ## same column used in create_centroids
  hex_size = 0.12,
  ## same size used in create_grid
  hex_filter = 10,
  use_neighbours = tas_sa2,
  focal_points = capital_cities %>%
    filter(points == "Hobart"),
  width = 35,
  verbose = FALSE
)

## Prepare to plot
fort_hex <- fortify_hexagon(data = hex_allocated,
                            sf_id = "sa2_name_2011",
                            hex_size = 0.12)

fort_tas <- tas_sa2 %>%
  fortify_sfc()

## Make a plot
library(ggplot2)
tas_hexmap <- ggplot() +
  geom_polygon(aes(
      x = long,
      y = lat,
      group = interaction(sa2_name_2011, polygon)
    ),
    fill = "white",
    colour = "lightgrey",
    data = fort_tas
  ) +
  geom_polygon(aes(
    x = long,
    y = lat,
    group = hex_id,
    fill = rownumber
  ),
  data = fort_hex) +
  scale_fill_distiller("", palette = "PRGn") +
  coord_equal() + theme_void()
tas_hexmap
\end{Sinput}
\end{Schunk}

\begin{Schunk}
\begin{Sinput}
###############################################################################

aus_grid <- gridExtra::grid.arrange(aus_ggchoro, aus_ggcont, aus_ggncont, aus_ggdorl, nrow = 2)

aus_grid
ggsave(filename = "figures/aus_grid.png", plot = aus_grid,
  device = "png", bg = "transparent", dpi = 300,  width = 7, height = 6)
\end{Sinput}
\end{Schunk}

\begin{figure}[h]
\centering
\includegraphics[width=14cm]{figs/nsw_grid.png}
\caption{\label{fig:nsw_grid}A collection of alternative maps of the Statistical Areas of Australia at Level 2. The colours communicate the value of the estimated SIR of Melanoma for males, ranging from much lower than average (blue) to much higher than average (red)}
\end{figure}

When communicating information that is relevant to the population, each
member of the population can be given equal representation by
transforming the map \citep{TVSSS}. The impact of a disease over
connected communities can be seen by allowing the boundaries to maintain
connection in the transformed display. The contiguous cartogram
displayed in figure \ref{fig:nsw_grid}b) draws attention to smaller
geographic units when they are rescaled according to the population
\citep{DMAHP}. These new shapes can now be coloured to represent a
second variable. This display can create twisted and unfamiliar shapes
from the geographic units as the algorithms must satisfy the topology
conditions, especially when there are communities located geographically
far from their neighbours \citep{TVSSS}. This shown in the northern SA2s
of New South Wales with an average (yellow) estimated SIR of Melanoma
for males.

The non-contiguous cartogram in figure \ref{fig:nsw_grid}c) also uses
the population to rescale the geographic units. Unlike the contiguous
cartogram, the SA2 areas maintain their geographic shape, but they may
not retain the connection with their neighbours. The population of the
SA2 areas is used to scale the geographic units in the non-contiguous
cartogram \citep{NAC}. The amount of white space can be meaningful in
non-contiguous cartograms \citep{ECGC}, in this example the disparity
between large rural areas and small urban areas means that the city of
Hobart, shown in the inset map looks reasonable, but these units are not
visible in the context of the New South Wales state map. Depending on
the difference between the population and geographic land size, the
amount of white space can also prevent meaningful understanding of the
distribution \citep{TVSSS}.

The Dorling cartogram presents each geographic unit as a circle, the
size of the circle is scaled according to the population value of each
area \citep{ACTUC}. Figure \ref{fig:nsw_grid}d) shows the New South
Wales SA2 areas as an individual circle located as close as possible to
the geographic centroid location. This map draws attention to the
collection of coastal cities in New South Wales that were not apparent
in figure \ref{fig:nsw_grid} a), b) or c).

@@

The following code creates the hexagon tile map for all the Statistical
Areas at Level 2 in New South Wales. These steps can be executed by the
main function, \texttt{create\_hexmap}, or can be implemented separately
for more flexibility.

@@

\begin{figure}[h]
\centering
\includegraphics[width=14cm]{figs/aus_gghexmap.png}
\caption{\label{fig:melanoma-hex}A hexagon tile map of the Statistical Areas of Australia at Level 2. The colours communicate the value of the estimated SIR, they range from much lower than average (blue) to much higher than average (red)}
\end{figure}

@@

The polygon set of Statistical Areas at Level 2 (SA2) \citep{abs2011} of
New South Wales in 2011 is provided with the \texttt{sugarbag} package
as \texttt{tas\_sa2}. A single column of the data set is used to
identify the unique areas. In this case, the unique SA2 names for each
SA2 have been used.

The longitude and latitude centre of the capital cities of Australia are
used as focal points to allocate each geographic area around the closest
capital city. Hobart will be the common focal point, as this example
uses only the areas in the state of New South Wales.

@@

\begin{figure}[h]
\centering
\includegraphics[width=14cm]{figs/1centroids.png}
\caption{\label{fig:centroids_plot}The geographic shapes of the Statistical Areas of New South Wales at Level 2. The points show the locations of the centroids of the SA2 areas.}
\end{figure}

@@

The distance between each centroid in the set, and each of the focal
points provided is calculated. The name of the closest focal point, and
the distance and angle from focal point to polygon centroid is joined to
polygon data set. To minimise time taken for this step only one option
is provided, New South Wales's capital city Hobart. The order for
allocation is determined by the distance between the polygon centroid
and it's closest focal point. The points are arranged from the centroid
closest to the focal point(s), to the furthest.

@@

\begin{figure}[h]
\centering
\includegraphics[width=16cm]{figs/6allocate.png}
\caption{\label{fig:buffs}A complete hexagon tile map of New South Wales.}
\end{figure}

A complete hexagon tile map of New South Wales is created by applying
the algorithm steps to each centroid. The hexagon tile map visualisation
is used below to visualise the Australian Cancer Atlas data
\citep{TACA}. Two views of the same data are produced by filling
according to the thyroid Cancer Standardised Incidence Rates (SIRs)
downloaded from the Australian Cancer Atlas site. This small example in
Figure \ref{fig:sir} shows the group of blue areas in the Hobart CBD
more prominently in the hexagon tile map (b). The small red areas
visible in the choropleth map (a) along the north coast are much larger
in the hexagon tile maps. The hexagon tile map shows less yellow, this
no longer overwhelms the map space with the information regarding the
rural areas.

@@

This algorithm has been applied to the complete set of all Australian
Statistical Areas at Level 2. This display highlights the density of
Australian capital cities, as it draws attention to the many communities
in Sydney, Melbourne and Hobart. This display also highlights the
disparity in the burden of Melanoma cancer for males in the communities
of these three cities. There are several collections of red hexagons in
Hobart that draw attention and they represent the communities with much
higher rates of diagnosis than the Australian average. The communities
south of Hobart show a gradient of colour as the values progress from
higher than average, to much lower than average for the communities
closer to the Sydney CBD. This pattern progresses into the communities
with lower than average rates in Melbourne and New South Wales.

@@

\begin{figure}[h]
\centering
\includegraphics[width=14cm]{figs/aus_gghexmap.png}
\caption{\label{fig:melanoma-geo}A hexagon tile map of the Statistical Areas of Australia at Level 2. The colours communicate the value of the estimated SIR of Melanoma for males, they range from much lower than average (blue) to much higher than average (red).}
\end{figure}

@@

These hexagons equally represent each area. However, the tessellation
does not allow the size of the hexagons to represent another variable,
similar to the choropleth maps. The algorithm is heavily dependent on
the focal points used, as this determines the order of allocation. It
works on the assumption that viewers can use directional relationships
to identify their neighbourhoods but this can be aided by the animation.
With careful consideration of the choropleth map, the small geographic
inner city areas may have been noticed by viewers, but the hexagon tile
map display emphasises them. The communities in northern New South Wales
and the Northern territory do not draw attention because of their size
as in the choropleth, but their colour is still noticeably below average
when contrasted with the hexagons further south.

The Dorling cartogram was the most influential in the design of the
hexagon tile map. The use of a hexagon provides a simple shape that
shifts the focus of the visualisation from the shape of SA2s to the
distribution effects of a disease on communities. not impeded by the
irregular and unusual shapes created by a contiguous cartogram and the
immense white space created on the non-contiguous cartogram. Hexagons
can emphasise the relationship between neighbouring communities by
allowing their sides to touch. The tessellation crated by adjoining
hexagons for densely populated areas is helpful as it shows that most
communities are not islands onto themselves, but are intrinsically
connected to those around them. As seen in the Dorling cartogram in
figure \ref{fig:nsw_grid}c), the tessellation that allows boundary
connections was not imposed for rural communities, where centroid of the
geographic unit was located far from others, a feature that allows
distant but dense populations of the coastal towns of New South Wales to
be recognised.

@@

\bibliography{sugarbag.bib}

>>>>

\begin{Schunk}
\begin{Sinput}
states <- absmapsdata::state2011 %>% 
  filter(!state_name_2011 == "Other Territories") %>% 
  rmapshaper::ms_simplify(keep = 0.25, keep_shapes = TRUE)

sa2 <- absmapsdata::sa22011 %>% 
  filter(state_name_2011 == "Tasmania") %>% 
  filter(!st_is_empty(geometry)) %>% 
  filter(!state_name_2011 == "Other Territories")

@@

aus_ggchoro <- ggplot(sa2thyroid_ERP) + 
  geom_sf(fill = "lightgrey", data = states %>% filter(state_name_2011=="Tasmania")) + 
  geom_sf(aes(fill = SIR)) + 
  scale_fill_identity() +invthm
\end{Sinput}
\end{Schunk}

\begin{Schunk}
\begin{Sinput}
## Create centroids set
centroids <- absmapsdata::sa22011 %>% 
  filter(!st_is_empty(geometry)) %>% 
  filter(state_name_2011 == "Tasmania") %>% 
 # filter(!sa2_name_2011 == "Lord Howe Island") %>% 
  create_centroids(., "sa2_name_2011")

## Create hexagon grid
grid <- create_grid(centroids = centroids,
                    hex_size = 0.2,
                    buffer_dist = 5)

## Allocate polygon centroids to hexagon grid points
hex_allocated <- allocate(
  centroids = centroids,
  hex_grid = grid,
  sf_id = "sa2_name_2011",
  ## same column used in create_centroids
  hex_size = 0.2,
  ## same size used in create_grid
  hex_filter = 10,
  focal_points = capital_cities,
  width = 35,
  verbose = FALSE
)

## Prepare to plot
fort_hex <- fortify_hexagon(data = hex_allocated,
                            sf_id = "sa2_name_2011",
                            hex_size = 0.2) %>% 
            left_join(sa2thyroid_ERP %>% select(sa2_name_2011, SIR, p50))

fort_aus <- sa2thyroid_ERP %>%
 # filter(!sa2_name_2011 == "Lord Howe Island") %>% 
  fortify_sfc()

fort_state <- states %>% 
  filter(state_name_2011 == "Tasmania") %>% 
  fortify_sfc() %>% 
  filter(long < 159)

## Make a plot
library(ggplot2)
aus_hexmap <- ggplot() +
  geom_polygon(aes(x = long,  y = lat, group = interaction(state_name_2011, polygon)),
               fill = "darkgrey",  data = fort_state) +
  geom_polygon(aes(x = long,  y = lat,  group = interaction(sa2_name_2011, polygon)),
               fill = "black",  colour = "darkgrey",  size = 0.1, data = fort_aus) +
  geom_polygon(aes(x = long, y = lat, group = hex_id, fill = SIR), data = fort_hex) +
  scale_fill_identity() +
  invthm + coord_equal()
aus_hexmap
\end{Sinput}

\includegraphics{kobakian-cook_files/figure-latex/fullhexmap-1} \end{Schunk}

\begin{Schunk}
\begin{Sinput}
sa2thyroid_ERP <- st_transform(sa2thyroid_ERP, 3112)
sa2thyroid_ERP <- sa2thyroid_ERP %>% 
  mutate(sva = sqrt(as.numeric(Population)/as.numeric(albers_sqkm)))

@@

aus_ggcont <- ggplot(cont) + 
  geom_sf(fill = "darkgrey",  data = states %>% st_transform(., 3112) %>% filter(state_name_2011 == "Tasmania")) +
  geom_sf(fill = "darkgrey",  data = sa2thyroid_ERP) +
  geom_sf(aes(fill = SIR), colour = NA) + 
  scale_fill_identity() + 
  invthm + guides(fill=FALSE)
aus_ggcont
\end{Sinput}

\includegraphics{kobakian-cook_files/figure-latex/alternatives-1} \begin{Sinput}
ggsave(filename = "figs/aus_ggcont.png", plot = aus_ggcont,
       device = "png", bg = "transparent", dpi = 300,  width = 7, height = 6)
\end{Sinput}
\end{Schunk}

@@

tas_ggncont <- ggplot(ncont %>% filter(state_name_2011 == "Tasmania")) + 
  geom_sf(fill = "darkgrey",  data = states %>% st_transform(., 3112) %>% filter(state_name_2011 == "Tasmania")) +
  geom_sf(fill = "darkgrey",  data = sa2thyroid_ERP) +
  geom_sf(aes(fill = SIR), colour = NA) + 
  scale_fill_identity() + 
  invthm + guides(fill=FALSE)
tas_ggncont
\end{Sinput}

\includegraphics{kobakian-cook_files/figure-latex/unnamed-chunk-1-1} \begin{Sinput}
# Hobart
hobart <- ggplot(ncont %>% filter(gcc_name_2011 == "Greater Hobart")) + 
  geom_sf(fill = "darkgrey",  data = sa2thyroid_ERP %>% filter(gcc_name_2011 == "Greater Hobart")) +
  geom_sf(aes(fill = SIR, size = 0.001), colour = "black") + 
  scale_fill_identity() + 
  scale_size_identity() +
  invthm + guides(fill=FALSE) + 
  theme(plot.background = element_rect(fill = "transparent", colour = NA)) + 
  theme(panel.background = element_rect(fill = "transparent", colour = "white"))

aus_ggncont <- ggdraw(xlim = c(0, 1), ylim = c(0, 2)) +
  draw_plot(tas_ggncont, width = 1, height = 2) +
  draw_plot(hobart, x = 0, width = 0.4, height = 0.4)
aus_ggncont
\end{Sinput}

\includegraphics{kobakian-cook_files/figure-latex/unnamed-chunk-1-2} \begin{Sinput}
ggsave(filename = "figs/aus_ggncont.png", plot = aus_ggncont,
       device = "png", bg = "transparent", dpi = 300,  width = 7, height = 6)
\end{Sinput}
\end{Schunk}

@@

dorl <- sa2thyroid_ERP %>%
  #mutate(pop = (Population/max(Population))*10) %>% # helpful for all of Australia
  cartogram_dorling(., weight = "Population", k = 0.2, m_weight = 1) %>% st_as_sf()
d <- st_bbox(dorl)
aus_ggdorl <- ggplot(dorl) +
  geom_sf(fill = "darkgrey",  data = states %>% st_transform(., 3112) %>% filter(state_name_2011 == "Tasmania")) +
  geom_sf(fill = "darkgrey",  data = sa2thyroid_ERP) + 
  geom_sf(aes(fill = SIR)) + 
  scale_fill_identity()+
  invthm + guides(fill = FALSE)
aus_ggdorl
\end{Sinput}

\includegraphics{kobakian-cook_files/figure-latex/unnamed-chunk-2-1} \begin{Sinput}
ggsave(filename = "figs/aus_ggdorl.png", plot = aus_ggdorl,
       device = "png", bg = "transparent", dpi = 300,  width = 7, height = 6)
\end{Sinput}
\end{Schunk}

\begin{Schunk}
\begin{Sinput}
aus_grid <- ggdraw(xlim = c(0, 2), ylim = c(0, 4)) +
  draw_plot(aus_ggchoro, x = 0, y = 2, width = 1, height = 2) +
  draw_plot(aus_ggcont,  x = 1, y = 2, width = 1, height = 2) +
  draw_plot(aus_ggncont, x = 0, y = 0, width = 1, height = 2) +
  draw_plot(aus_ggdorl,  x = 1, y = 0, width = 1, height = 2)

aus_grid
\end{Sinput}

\includegraphics{kobakian-cook_files/figure-latex/mapgrid-1} \begin{Sinput}
ggsave(filename = "figs/aus_grid.png", plot = aus_grid,
  device = "png", bg = "transparent", dpi = 300, width = 8, height = 10)
\end{Sinput}
\end{Schunk}

When communicating information that is relevant to the population, each
member of the population can be given equal representation by
transforming the map \citep{TVSSS}. The impact of a disease over
connected communities can be seen by allowing the boundaries to maintain
connection in the transformed display. The contiguous cartogram
displayed in figure \ref{fig:nsw_grid}b) draws attention to smaller
geographic units when they are rescaled according to the population
\citep{DMAHP}. These new shapes can now be coloured to represent a
second variable. This display can create twisted and unfamiliar shapes
from the geographic units as the algorithms must satisfy the topology
conditions, especially when there are communities located geographically
far from their neighbours \citep{TVSSS}. This shown in the northern SA2s
of Tasmania with an average (yellow) estimated SIR of Melanoma for
males.

The non-contiguous cartogram in figure \ref{fig:nsw_grid}c) also uses
the population to rescale the geographic units. Unlike the contiguous
cartogram, the SA2 areas maintain their geographic shape, but they may
not retain the connection with their neighbours. The population of the
SA2 areas is used to scale the geographic units in the non-contiguous
cartogram \citep{NAC}. The amount of white space can be meaningful in
non-contiguous cartograms \citep{ECGC}, in this example the disparity
between large rural areas and small urban areas means that the city of
Hobart, shown in the inset map looks reasonable, but these units are not
visible in the context of the Tasmania state map. Depending on the
difference between the population and geographic land size, the amount
of white space can also prevent meaningful understanding of the
distribution \citep{TVSSS}.

The Dorling cartogram presents each geographic unit as a circle, the
size of the circle is scaled according to the population value of each
area \citep{ACTUC}. Figure \ref{fig:nsw_grid}d) shows the Tasmania SA2
areas as an individual circle located as close as possible to the
geographic centroid location. This map draws attention to the collection
of coastal cities in Tasmania that were not apparent in figure
\ref{fig:nsw_grid} a), b) or c).

@@

The following code creates the hexagon tile map for all the Statistical
Areas at Level 2 in Tasmania. These steps can be executed by the main
function, \texttt{create\_hexmap}, or can be implemented separately for
more flexibility.

@@

\begin{Schunk}
\begin{Sinput}
aus_hexmap
\end{Sinput}
\end{Schunk}

@@

The polygon set of Statistical Areas at Level 2 (SA2) \citep{abs2011} of
Tasmania in 2011 is provided with the \texttt{sugarbag} package as
\texttt{tas\_sa2}. A single column of the data set is used to identify
the unique areas. In this case, the unique SA2 names for each SA2 have
been used.

The longitude and latitude centre of the capital cities of Australia are
used as focal points to allocate each geographic area around the closest
capital city. Hobart will be the common focal point, as this example
uses only the areas in the state of Tasmania.

@@

\begin{figure}[h]
\centering
\includegraphics[width=14cm]{figs/1centroids.png}
\caption{\label{fig:centroids_plot}The geographic shapes of the Statistical Areas of Tasmania at Level 2. The points show the locations of the centroids of the SA2 areas.}
\end{figure}

@@

The distance between each centroid in the set, and each of the focal
points provided is calculated. The name of the closest focal point, and
the distance and angle from focal point to polygon centroid is joined to
polygon data set. To minimise time taken for this step only one option
is provided, Tasmania's capital city Hobart. The order for allocation is
determined by the distance between the polygon centroid and it's closest
focal point. The points are arranged from the centroid closest to the
focal point(s), to the furthest.

@@

\begin{figure}[h]
\centering
\includegraphics[width=16cm]{figs/6allocate.png}
\caption{\label{fig:buffs}A complete hexagon tile map of Tasmania.}
\end{figure}

A complete hexagon tile map of Tasmania is created by applying the
algorithm steps to each centroid. The hexagon tile map visualisation is
used below to visualise the Australian Cancer Atlas data \citep{TACA}.
Two views of the same data are produced by filling according to the
thyroid Cancer Standardised Incidence Rates (SIRs) downloaded from the
Australian Cancer Atlas site. This small example in Figure \ref{fig:sir}
shows the group of blue areas in the Hobart CBD more prominently in the
hexagon tile map (b). The small red areas visible in the choropleth map
(a) along the north coast are much larger in the hexagon tile maps. The
hexagon tile map shows less yellow, this no longer overwhelms the map
space with the information regarding the rural areas.

@@

This algorithm has been applied to the complete set of all Australian
Statistical Areas at Level 2. This display highlights the density of
Australian capital cities, as it draws attention to the many communities
in Sydney, Melbourne and Hobart. This display also highlights the
disparity in the burden of Melanoma cancer for males in the communities
of these three cities. There are several collections of red hexagons in
Hobart that draw attention and they represent the communities with much
higher rates of diagnosis than the Australian average. The communities
south of Hobart show a gradient of colour as the values progress from
higher than average, to much lower than average for the communities
closer to the Sydney CBD. This pattern progresses into the communities
with lower than average rates in Melbourne and Tasmania.

@@

@@

These hexagons equally represent each area. However, the tessellation
does not allow the size of the hexagons to represent another variable,
similar to the choropleth maps. The algorithm is heavily dependent on
the focal points used, as this determines the order of allocation. It
works on the assumption that viewers can use directional relationships
to identify their neighbourhoods but this can be aided by the animation.
With careful consideration of the choropleth map, the small geographic
inner city areas may have been noticed by viewers, but the hexagon tile
map display emphasises them. The communities in northern Tasmania and
the Northern territory do not draw attention because of their size as in
the choropleth, but their colour is still noticeably below average when
contrasted with the hexagons further south.

The Dorling cartogram was the most influential in the design of the
hexagon tile map. The use of a hexagon provides a simple shape that
shifts the focus of the visualisation from the shape of SA2s to the
distribution effects of a disease on communities. not impeded by the
irregular and unusual shapes created by a contiguous cartogram and the
immense white space created on the non-contiguous cartogram. Hexagons
can emphasise the relationship between neighbouring communities by
allowing their sides to touch. The tessellation crated by adjoining
hexagons for densely populated areas is helpful as it shows that most
communities are not islands onto themselves, but are intrinsically
connected to those around them. As seen in the Dorling cartogram in
figure \ref{fig:nsw_grid}c), the tessellation that allows boundary
connections was not imposed for rural communities, where centroid of the
geographic unit was located far from others, a feature that allows
distant but dense populations of the coastal towns of Tasmania to be
recognised.

@@

\bibliography{kobakian-cook.bib}
